\chapter{Optimization modeling via Quantum Computer}

\section{Introduction}


\subsection{QUBO}


\subsection{Ising model}

\section{Modeling}

The strategy to solve the binary optimization problem
is mapping a binary state as spin-$1/2$ qubits states.
There are two type of binary problem by the permitted values
of the state, $\{0, 1\}$ problem and $\{-1, 1\}$ problem.
The two problems are identical.
We can make a well-defined transformation.

\begin{equation}
    \{0, 1\} \leftrightarrow \{-1, 1\}
\end{equation}

Let, $z \in \{-1, 1\}$ and $x \in \{0, 1\}$, 

\begin{example} Transformation of binary value.

    \begin{equation*}
        z_i = \frac{1}{2}(1- x_i)
    \end{equation*}
\end{example}

\begin{exercise}
    
    Make a formula of binary transformations about next two transformation.

    \begin{equation*}
        f(x)_{\rightarrow} \begin{cases}
            0 & \mbox{if } x=-1 \\
            1 & \mbox{otherwise}
        \end{cases}
    \end{equation*}

    \begin{equation*}
        f(z)_{\rightarrow} \begin{cases}
            -1 & \mbox{if } z=0 \\
            1 & \mbox{otherwise}
        \end{cases}
    \end{equation*}
\end{exercise}



\begin{equation}
x_i = \frac{1}{2}(1-z_i)
\end{equation}

\subsection{Max-cut}

\begin{definition}Max-cut problem

    For a given graph, $G=(V,E)$, we define a \textbf{cut} as an edge whose ends are in different partition of vertex.
    Find a 2 partition of vertex, $V$ whose number of cut is maximized in the graph.
\end{definition}


It is a well-known NP-hard problem in computer science. 
There is no polynomial algorithm to solve the problem for arbitrary graph.

\begin{example} Portfolio Optimization problem

    Hedging is a fundamental method to avoid a loss in financial management.
    It is widely adopted principle not only for professional market traders,
    but also for individuals.
    
    Many products in the market have been well-analyzed about their 
    relationship. For example, when one product become higher or lower valued 
    by the situation, we could not predict an exact price of related products,
    but at least their asymptotic range of value change.

    The strategy of portfolio optimization preventing loss is finding 
    a combination that has a minimum relation between the internal elements.
    
\end{example}
\subsection{Max-Clique}

\subsection{Restricted Problem}

Many practical problems are required to meet specific constraints,
such as number of vertices must be 3 or 5 in the problem.

\subsubsection{Node number restriction}

The next term makes a quadratic energy state as $(x-\mu)^2$.

\begin{equation*}
    H = (\frac{1}{2}\sum_{i} (I - Z_i) - \mu I)^2
\end{equation*}


\section{Optimization method}

From the above sections, we reviewed some mapping that graph optimization problems 
could be modeled as ising Hamiltonians.
Unlikely, the graph optimization problem, a quantum system eventually fall into a ground state 
with proper environment condition. In addition, these processes are already known in quantum mechanics.
Finding a ground state energy of the system is directly related to specific optimization problem.

The reverse direction has been widely used in quantum simulation. 
In density functional theory, we optimize a specific functional to reach an optimal point
using computational methods. 
We can attempt this method for solving various optimization problems.


