\chapter{Imaginary Time evolution}


\section{Imaginary time}

Imaginary time evolution is frequently used in 
quantum system simulation especially, in statistical 
physics. 
In the statistical mechanics it is called by 
\textit{Diffusion Montecarlo method}. 
The reason is that from the Schr$\ddot{\mbox{o}}$dinger equation,
we can directly obtain a progress to reach the ground state of the system.
From the time-independent Schr$\ddot{\mbox{o}}$dinger equation, 

\begin{equation}
    i \hbar \frac{\partial}{\partial}| \psi \rangle = H |\psi \rangle
\end{equation}

takes $\tau = i t$  then, $df/d\tau = (dt/d\tau) df/dt = i df/dt$, thus,

\begin{align}
    \frac{\partial}{\partial \tau} | \psi \rangle = H | \psi \rangle \label{eq:imginary_sch_eq}\\
    | \psi(\tau) \rangle = e^{- \tau H} | \psi(0) \rangle
\end{align}

From the Eq (\ref{eq:imginary_sch_eq}), we get a general solution,

\begin{equation}
    |\Psi \rangle = \sum_{i} c_i(0) e^{- E_i \tau} | \psi_i \rangle
\end{equation}

The terms are decaying and does not oscillate. Therefore, with sufficient long time, $\tau$, 
we get 

\begin{equation}
    |\Psi(\tau) \approx_{\tau \rightarrow \infty} c_g(0) e^{- E_g \tau} | \psi_g \rangle
\end{equation}

However, the imaginary time evolution cannot be directly 
implemented in common gate model computer. 
Since, it is a non-unitary transformation, $\exp(-H \tau)^\dagger = \exp(-H \tau)$, Hermit. 
Therefore, the implementation of ITE is also a challenge in the quantum computation.
There are several ways, one is approximate the non-unitary gate with unitary gate.
It is a common method by VQE, we can approximate unitary process to reach the same result 
of the imaginary time steps. 
The other methods are a block-encoding, embeding the non-unitary gate into unitary gate, or
using a measurement based approach. 
The method we used in the implementation was non-unitary Trotter circuit suggested by Leadbeater et al\cite{leadbeater_non-unitary_2023}.
Once we get a proper ITE routine, then the quantum computer could find a ground state from 
the \textit{given} states.

\section{Non-unitary on unitary}

There are many method to obtain non-unitary
operation on unitary system.
\subsection{Embeding in unitary}

Even the whole gate was unitary,
their sub-block matrix could be non-unitary.
Using an ancilla register, we can obtain a
non-unitary operation on the main register.

Especially, the measurement based 
operation suggested by 
is based on Trotterization.


\subsection{VQE approximation}

\section{Spectrum Search}