\chapter{Variational method}

It is considered practically useful method in
NISQ era\footnote{Noisy intermediate scale quantum era}.


Review \cite{cerezo_variational_2021}.
\section{Introduction}

\subsection{Variatiaonal Principle}

\subsection{Circuit as ansatz}

The term \textit{ansatz} means an assumption 
in mathematics or physics to solve the given problem.
In the physics, it is commonly refer a model representing 
or containing the solution of the problem.
The statement of \textit{Is the ansatz proper to solve the problem?}
refers the whether is it possible that "The solution could be represented with the model"
or, in optimization problem, "The ansatz achive the desire solution".

Using a paramerized circuit, we can treat the quantum circuit 
as a neural network in machine leanring. 
However, if the result is not bounded, 
the optimization is meaningless for any kinds purpose.
That is why we need a \textit{Variational principle}.
Since, quantum circuit is a kind of quantum system and their
ground state and energy is limited in finite value.
Same statement holds for parameterized circuit, there always 
exists a ground state energy\footnote{Not a state. There could be degenerated states.}.

Whatever energy we measure from quantum circuit, it is always higher or equal with the ground state.

\begin{equation*}
    E_{ground} \leq \langle \psi | H | \psi \rangle
\end{equation*}


We can optimize the circuit without any worry about their convergence.


\begin{principle}
    \textbf{Variational Principle}

    \begin{equation}
        E_{g} \leq \langle \psi | H | \psi \rangle \leq E_{\mbox{max}}
    \end{equation}
\end{principle}

\subsection{Universality of Circuit}

One of the strong background of the neural network model is 
\textit{Universal Approximation Theorem}. 

How about quantum circuit? Do we have any those type of theorem?
The answer is yes!. Quantum circuit is also a universal approximator.
In addition, it is more powerful. Even with a single qubit we can achieve the property\cite{PhysRevA.104.012405-Universal-approxi}.

\section{}

\section{Ansatzs}

\subsection{Hardware Efficient}

\subsection{Evolution Based Ansatz}

\subsubsection{QAOA Ansatz}

Suppose we solve a binary optimization problem.
In this case, we can formulate the problem with ising-like Hamilotnian whose terms only have $Z$ and $I$.
In the case, one approach is an adiabatic process to find a ground state.
Let a initial Hmailtonian as $\sum_i X_i$ whose ground state is well-known.

\begin{equation}
    H_i = -\sum_i X_i, H_f = \mu_0\sum_i Z_i + \mu_1 \sum_{i, j}  Z_i Z_j
\end{equation}

In adiabatic process, any Hamiltonian applied in the process, $H(t)$ would be a mixture of the two Hamiltonian.
We can expect the circuit would well approximate the evolution of intermediate Hamiltonian of any time $t$.

\begin{center}
    $\begin{quantikz}
        &\gate{H}&\\
        &\gate{H}&\\
        &\wave& \\
        &\gate{H}&\\
    \end{quantikz} $$\rightarrow$
    \begin{quantikz}
        &\gate{RX(\theta_0)}&\gate{RZ(\phi_0)}&\\
        &\gate{RX(\theta_1)}&\gate{RZ(\phi_1)}&\\
        &\wave& &\\
        &\gate{RX(\theta_n)}&\gate{RZ(\phi_n)}&\\
    \end{quantikz}
\end{center}

\section{Application}

\subsection{QUBO}

\subsection{Evolution}

\subsubsection{Real time}

\subsubsection{Imaginary time}

\section{Implementation}

\subsection{Pennylane}

\subsection{Qiskit}

\bibliographystyle{unsrt}
\bibliography{vqe}

