\documentclass[10pt]{book}
\usepackage{NotesTeXV3,lipsum}
% tikz is in the style file
\usetikzlibrary{calc, angles, quotes}
\usetikzlibrary{quantikz2}
\newcommand{\AxisRotator}[1][rotate=0]{%
    \tikz [x=0.25cm,y=0.60cm,line width=.2ex,-stealth,#1] \draw (0,0) arc (-150:150:1 and 1);%
}
\usepackage{pgf}
\usepackage{pgfmath}
\usetikzlibrary{shapes.geometric, math}

\usepackage{imakeidx}
\makeindex

\title{
    Materials for the simulation of quantum system behavior on quantum computer}
\author{Hyunseong Kim}
\emailAdd{qwqwhsnote@gm.gist.ac.kr}

\begin{document}
\maketitle
\newpage
\pagestyle{fancynotes}

\section*{Preface}

This document is a cheet-sheet and proof-notes about 
quantum simulation on quantum computer, especially, in gate model.
If you know basic postulations and concepts of quantum computers and you want to implement the simulation
of the given quantum system, it might be helpful. 

Mainly focusing on Product-formula method and its optimization topics. 
They are basic materials for any kinds of quantum simulation and my Bachelor thesis subject.
The formalization part is a basic materials for the product formula implementation
minimizing errors on the formulation steps.
The mathematical background of the evolution circuit and their representations were dicsussed.
Optimization part is about the optimize the evolution circuit by using various techniques.
In the practical part, we review the many practical techniques using quantum 
computer and their simple implementations. 
The modeling of the single-particle system, adiabatic process implementation, 
VQE introduction are dicussed.
In the further topics part, we reviewed the advanced topics. 
Using 1 dim particle simulator, we dicussed about tunneling phanomenon and their 
simulation in quantum computer.
Material modeling and physcial properties simulation in many-body physics,
binary optimization in quantum computer briefly reviewed.

Written programs and algorithm implemnetations are also provided with refering repositories.
In appendix, step by step example of simulation and measurement 
using some popular quantum frameworks;Qiskit, Pennylane, D-Wave et cetra.


Most contents are related with author's studies and research in the course of Quantum Graduate School internship
established by 8 university. Thanks for Dr. Kim(GIST), Dr. Yee(GIST) and Dr. Choi(Korea).

\begin{itemize}
    \item 2023 Summer Special Internship, held by Korea university
    \item Bachelor research internship on Quantum Field and Gravitation Lab of GIST
    \item Bachelor research internship on Computational Material Lab of GIST
\end{itemize}

Abbrevations

\begin{itemize}
    \item QC: Quantum computation
    \item CC: Classcial computation
\end{itemize}

\newpage

\part{Simulation of Quantum system}
\chapter{Formalization and Evolution}

\input{parts/formalization/discretization.tex}
\input{parts/formalization/time_evolution_operator.tex}
\input{parts/formalization/circuit_representation.tex}
%======================================================================================================================================

\newpage
\chapter{Optimization of evolution circuit}
\input{parts/optimization/optimization_circuit.tex}

%=====================================================================================================================================
\newpage
\part{Practical Examples}

\input{parts/practical/basic_simulation.tex}
\input{parts/practical/adiabatic_simulation.tex}
\input{parts/practical/imaginary_evolution.tex}
\input{parts/practical/VQE.tex}
\input{parts/practical/Material_simulation.tex}
\input{parts/practical/ttp.tex}

%===================================
\newpage
\part{Further Topics}
\input{parts/further_topics/simulation.tex}
%======================================================================================================================================
\newpage
\bibliographystyle{unsrt}
\bibliography{references.bib}

%======================================================================================================================================
\newpage
\part{Appendix}
\appendix

\input{appendix/unitary-hermite.tex}
\input{appendix/notation_int_qc.tex}
\input{appendix/fourier_transformation.tex}
\input{appendix/pauli_polynomial.tex}
\input{appendix/mathematics.tex}
\input{appendix/NP-problems.tex}

Additional topic: time evolution operator of Hamiltonian,


\printindex

\end{document}